BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-13 tex/5-evaluation.tex
Up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}

Beside the extraction of blog post date that we have been discussing so far, it is also interesting to go one step further and preserve the design of webpages. One of the initial blog forever requirements is to be able to save blogs such that future generation could see them as they were originally when first crawled by the system.

To achieve this property, our final solution was to embed a full web browser into our system, as presented in section *, which we use to take screen-shots of pages. Before choosing this tool we considered 3 other solutions: wget, wkhtmltopdf, oxpath. This subsection relates our evaluation of these tools for the specific purpose.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Preservation of blog visuals}
\TODO{visuals/design/graphic/?}

In addition to the extraction of blog content that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals. Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}.

As presented in section \autoref{techniques}, our crawler uses a full web browser to render pages.

To achieve this property, our final solution was to embed a full web browser into our system, , which we use to take screen-shots of pages. Before choosing this tool we considered 3 other solutions: wget, wkhtmltopdf, oxpath. This subsection relates our evaluation of these tools for the specific purpose.

@@

\cmark
\xmark
